---
title: "Lab 07 - Conveying the right message through visualisation"
author: "Tiffani J. Hill"
date: "February, 26, 2026"
output: github_document
---

### Load packages and data

```{r load-packages, message=FALSE}
library(tidyverse) 
```

### Exercise 1
```{r reading-data}
df <- read_csv("/Users/tiffani/Documents/GitHub/lab_07_betterviz/kansas_grouped_rolling_avg.csv")
```

### Exercise 2
```{r better-plot}
ggplot(df, aes(x = date, y = rolling_avg,
               color = mask_mandate)) +
  geom_point() +
   scale_y_continuous(breaks = c(0, 5, 10, 15, 20))
  labs(title = "COVID Cases By Mask Usage",
       y = "Average Number of Cases")
```

### Exercise 3
The visualization standardizes the y axis and shows that the COVID cases were lower for those who did not wear a mask. While this is the same data used in the original graph, it was misleading because the values on the y-axis for the mask-wearers were larger than the non-mask wearers. 

###Exercise 4
My visualization tells us that there were more documented COVID cases for people that wear masks than those that don't. However, I think this is also misleading because the people who wear masks likely get tested as higher rates than those that don't.

###Exercise 5
With the scales being equivalent, we see that the original visualization was very misleading. My accurate visualization shows that mask-wearers test positive for COVID-19 more than non-mask wearers. The only change I made was the labeling of the axes since that was the main aspect that was misleading.

###Exercise 6
This plot conveys the message that masking reduces covid cases over time. I removed the data from the people who don't wear masks. 
###Exercise 7
```{r different-plot}
df %>% 
  filter(mask_mandate == "Mask") %>% 
ggplot(aes(x = date, y = rolling_avg,
               color = mask_mandate)) +
  geom_smooth() +
   scale_y_continuous(breaks = c(0, 5, 10, 15, 20)) +
  labs(title = "COVID Cases By Mask Usage",
       y = "Average Number of Cases")
```

